Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
typo
fix anglais

\citet{DBLP:conf/pldi/GulwaniZ10} propose a technique for computing disjunctive invariants, by
distinguishing all the paths inside a loop. In
this section, we propose to improve this technique by using SMT queries to find
interesting paths, the objective being to avoid an explicit exhaustive
enumeration of an exponential number of paths.

For a loop header $p_i$, this technique computes a disjunctive invariant
$\bigvee_{1\leq j \leq m} X_{i,j}$. 
To do so, one chooses an integer $\delta \in [1,m]$, and
a mapping function $\sigma: [1,m] \times [1,n] \mapsto [1,m]$, assuming there
are $n$ distinct paths in the loop.  For each
abstract value of the disjunctive invariant, and for each path $\tau_{i,k}$ in the loop, the
image of $X_{i,j}$ by the path is joined with
$X_{i,\sigma(j,k)}$.
Initially, the $\delta$-th abstract value is assigned to the initial states of
$p_i$, and each other abstract value is assigned to bottom.

>>>>

\citet{DBLP:conf/pldi/GulwaniZ10} proposed a technique for computing disjunctive invariants, by
distinguishing all the paths inside a loop. In
this section, we propose to improve this technique by using SMT queries to find
interesting paths, the objective being to avoid an explicit exhaustive
enumeration of an exponential number of paths.

For a loop header $p_i$, this technique computes a disjunctive invariant
$\bigvee_{1\leq j \leq m} X_{i,j}$. 
To do so, one chooses an integer $\delta \in [1,m]$, and
a mapping function $\sigma: [1,m] \times [1,n] \mapsto [1,m]$, assuming there
are $n$ distinct paths in the loop.  For each
abstract value of the disjunctive invariant, and for each path $\tau_{i,k}$ in the loop, the
image of $X_{i,j}$ by the path is joined with
$X_{i,\sigma(j,k)}$.
Initially, the $\delta$-th abstract value contains the initial states of
$p_i$, and all other abstract values contain~$\emptyset$.
